%-------------------------
% Resume 
% Author : Pius Dan Nyongesa
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{\href{https://github.com/piusdan}{\Huge Pius Dan Nyongesa}} \\[4pt]
  \textbf{\large Senior Backend Engineer / Platform Engineer} \\[8pt]
  \small
  \faMapMarker\ Nairobi, Kenya \quad
  \faEnvelope\ \href{mailto:npiusdan@gmail.com}{npiusdan@gmail.com} \quad
  \faPhone\ +254 703 554 404 \\[2pt]
  \faGithub\ \href{https://github.com/piusdan}{github.com/piusdan} \quad
  \faLinkedin\ \href{https://www.linkedin.com/in/piusdannyongesa/}{linkedin.com/in/piusdannyongesa}
\end{center}

%-----------Professional Summary-----------------
\section{Professional Summary}
Senior Backend Engineer with 7+ years of experience designing, building, and operating high-scale, cloud-native backend systems and APIs. Proven track record of owning production microservices, data platforms, CI/CD pipelines, and distributed systems used by millions of users globally. Deep expertise in .NET (C\#), Azure, event-driven architecture, and microservices. Strong focus on performance, reliability, security, and long-term maintainability.

%-----------Core Backend & Platform Skills-----------------
\section{Core Backend \& Platform Skills}
\textbf{Languages:} C\#, .NET, Python, TypeScript \\
\textbf{Backend:} REST APIs, Microservices, Event-Driven Architecture \\
\textbf{Databases:} SQL, NoSQL (Cosmos DB), Data Pipelines \\
\textbf{Cloud \& Infra:} Azure, Kubernetes, Docker, GCP \\
\textbf{Messaging:} Azure Service Bus, Event Grid, MassTransit \\
\textbf{DevOps:} CI/CD, Azure DevOps, Git, Infrastructure as Code (Bicep) \\
\textbf{Observability:} Monitoring, Logging, Tracing, ELK Stack \\
\textbf{Architecture:} Distributed Systems, Fault Tolerance, Resilience, Scalability

%-----------Experience-----------------
\section{Professional Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Microsoft}{Nairobi, Kenya}
    {Software Engineer (Backend \& Platform)}{May 2019 -- Present}
    \resumeItemListStart
      \item\small{Designed and built high-scale backend microservices in C\#/.NET supporting AI-powered Copilot workflows across Microsoft business units.}
      \item\small{Built event-driven data ingestion and processing pipelines integrating LLMs with internal knowledge bases, serving millions of requests per day.}
      \item\small{Developed and maintained REST APIs and backend orchestration services for automation and data processing.}
      \item\small{Owned backend architecture for automated testing infrastructure running thousands of Windows application compatibility tests daily.}
      \item\small{Built self-healing distributed systems with automated failure detection, rollback, and recovery.}
      \item\small{Designed ring-based CI/CD deployments across multiple Azure regions with zero-downtime releases.}
      \item\small{Implemented system observability, monitoring, and alerting to ensure high availability and performance.}
      \item\small{Led architecture discussions, technical design reviews, and mentored junior engineers.}
    \resumeItemListEnd
    \textbf{Tech Stack:} C\#, .NET, Azure Functions, Service Bus, Event Grid, Cosmos DB, MassTransit, Azure DevOps, Bicep

  \resumeSubheading
    {Loanbee Limited}{Nairobi, Kenya}
    {Software Engineer (Backend)}{Jun 2018 -- May 2019}
    \resumeItemListStart
      \item\small{Built a cloud-native fintech lending platform using microservices architecture deployed on Kubernetes.}
      \item\small{Designed backend services for loan origination, credit scoring, and payments processing.}
      \item\small{Integrated mobile money transaction data into alternative credit scoring models, reducing default rates by 15\%.}
      \item\small{Built real-time observability platform using Elasticsearch, Kibana, and Logstash.}
      \item\small{Implemented service resilience using Istio service mesh with mTLS, retries, and fault tolerance.}
    \resumeItemListEnd
    \textbf{Tech Stack:} Python, Kubernetes, Docker, Istio, GCP, ELK Stack, Microservices

  \resumeSubheading
    {Africa's Talking}{Nairobi, Kenya}
    {Software Developer}{Apr 2017 -- Jun 2018}
    \resumeItemListStart
      \item\small{Built backend APIs for USSD, SMS, billing, and event ticketing platforms.}
      \item\small{Developed high-volume messaging systems serving 10,000+ users.}
      \item\small{Integrated telecom APIs for payments, airtime, and messaging.}
      \item\small{Built public participation and civic engagement platforms using USSD and SMS.}
    \resumeItemListEnd
    \textbf{Tech Stack:} Python, Flask, Django, USSD, SMS, API Integrations
\resumeSubHeadingListEnd

%-----------Selected Systems & Products-----------------
\section{Selected Systems \& Products}
\resumeSubHeadingListStart
  \resumeSubItem{Copilot AI Platform (Microsoft)}{Backend data ingestion and orchestration layer for enterprise AI workflows.}
  \resumeSubItem{Loanbee Lending Platform}{Fintech credit and payments backend serving thousands of borrowers.}
  \resumeSubItem{RoboPal AI}{WhatsApp-based AI education platform serving 10,000+ learners across Africa. \href{https://robopal.co}{robopal.co}}
  \resumeSubItem{ChangaChanga}{Multi-channel fintech payments platform integrated with Visa 3D and core banking systems. \href{https://changachanga.co.ke}{changachanga.co.ke}}
  \resumeSubItem{Kapu WhatsApp Shopping}{WhatsApp commerce backend driving 10\% weekly GMV growth. \href{https://kapuafrica.com}{kapuafrica.com}}
\resumeSubHeadingListEnd

%-----------Backend Architecture & System Design-----------------
\section{Backend Architecture \& System Design}
\resumeSubHeadingListStart
  \resumeSubItem{Event Processing}{Designed distributed backend systems processing millions of events per day.}
  \resumeSubItem{Fault Tolerance}{Built fault-tolerant microservices using retries, circuit breakers, and automated recovery.}
  \resumeSubItem{Zero-Downtime Deployments}{Implemented zero-downtime deployments with ring-based rollout strategies.}
  \resumeSubItem{Event-Driven Pipelines}{Designed scalable event-driven pipelines for AI and fintech platforms.}
  \resumeSubItem{Security}{Built secure, cloud-native systems with identity, encryption, and service-to-service authentication.}
\resumeSubHeadingListEnd

%-----------Publications & Speaking-----------------
\section{Publications \& Speaking}
\resumeSubHeadingListStart 
  \resumeSubItem{Kubernetes Security Publication}{Securing Kubernetes Clusters in the Cloud. \href{https://piusdan.medium.com/kubernetes-security-faf59ac121e1}{medium.com}}
  \resumeSubItem{Speaker — GDG Nairobi}{Running reliable Kubernetes platforms at scale.}
  \resumeSubItem{Speaker — PyCon}{Building fast microservices using gRPC.}
  \resumeSubItem{USSD Tutorial}{Open-source USSD development guide. \href{https://github.com/piusdan/USSD-Python-Demo}{github.com/piusdan/USSD-Python-Demo}}
\resumeSubHeadingListEnd

%-----------Education-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Jomo Kenyatta University of Science and Technology}{2015 -- 2021}
    {Bachelor of Science in Computer Science}{}
\resumeSubHeadingListEnd

%-----------Leadership & Community-----------------
\section{Leadership \& Community}
\resumeSubHeadingListStart  
  \resumeSubItem{Founder — Silicon Blaze}{
    Founded a nonprofit teaching computer science to economically disadvantaged youth. Led 20 volunteers and trained 1,000+ students across Kenyan high schools.
    \href{https://siliconblazeblog.wordpress.com/}{siliconblazeblog.wordpress.com}
  }
\resumeSubHeadingListEnd

%-----------Languages-----------------
\section{Languages}
English, Kiswahili

\end{document}